---
title: "Analysen zur Vorbereitung des MZP 2"
subtitle: "Kürzung der Tests"
author:
  - name: "Jürgen Schneider"
    email: "ju.schneider@dipf.de"
    affiliation: "DIPF"
    correspondence: true
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  eval: true
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: ceruleanc
    number-sections: true
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 3
    embed-resources: true # will make standalone html file
    code-fold: true
    code-tools: true
    code-link: true
editor_options: 
  chunk_output_type: console
---

```{r load packages}
#| echo: false

library(tidyverse)
library(lavaan)
library(psych)
library(here)
library(rio)
```


# Preparation



## Import & wrangle data

```{r import data sets}
ALK_K4_MZP1 <- rio::import(here("data/ALK_K4_220324.sav"))
LAA_K4_MZP1 <- rio::import(here("data/LAA_MZP1_241023.csv"))
SAB_K4_MZP1 <- rio::import(here("data/SAB_K4_110324.sav"))
```


```{r}
############################################################################## #
##### KODIERUNG DER TPK ITEMS IN RICHTIG/FALSCH                             ####
##### (Bei LAA ist dies noch nicht codiert)                                    #
############################################################################## #


#### Skript 11a TPK-Test Kodierung ########################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    tpksit1_2C = case_when( 
      #Es wird ein Punkt vergeben, wenn die falsche Option NICHT ausgewählt wurde.
      is.na(TPKSIT1_2) ~ 1,
      TPKSIT1_2 == 1 ~ 0),
    tpksit1_3C = case_when(
      is.na(TPKSIT1_3) ~ 1,
      TPKSIT1_3 == 1 ~ 0),
    tpksit1_4C = case_when(
      is.na(TPKSIT1_4) ~ 1,
      TPKSIT1_4 == 1 ~ 0),
    tpksit1_5C = case_when(
      is.na(TPKSIT1_5) ~ 1,
      TPKSIT1_5 == 1 ~ 0),
    tpksit1_7C = case_when(
      is.na(TPKSIT1_7) ~ 1,
      TPKSIT1_7 == 1 ~ 0),
    tpksit1_8C = case_when(
      is.na(TPKSIT1_8) ~ 1,
      TPKSIT1_8 == 1 ~ 0),
    tpksit1_1C = case_when( 
      #Es wird ein Punkt vergeben, wenn die richtige Option ausgewählt wurde.
      TPKSIT1_1 == 1 ~ 1,
      is.na(TPKSIT1_1) ~ 0),
    tpksit1_6C = case_when(
      TPKSIT1_6 == 1 ~ 1,
      is.na(TPKSIT1_6) ~ 0),
    
    tpksit9_1C = case_when(
      is.na(TPKSIT9_1) ~ 1,
      TPKSIT9_1 == 1 ~ 0),
    tpksit9_2C = case_when(
      is.na(TPKSIT9_2) ~ 1,
      TPKSIT9_2 == 1 ~ 0),
    tpksit9_3C = case_when(
      is.na(TPKSIT9_3) ~ 1,
      TPKSIT9_3 == 1 ~ 0),
    tpksit9_4C = case_when(
      is.na(TPKSIT9_4) ~ 1,
      TPKSIT9_4 == 1 ~ 0),
    tpksit9_7C = case_when(
      is.na(TPKSIT9_7) ~ 1,
      TPKSIT9_7 == 1 ~ 0),
    tpksit9_5C = case_when(
      TPKSIT9_5 == 1 ~ 1,
      is.na(TPKSIT9_5) ~ 0),
    tpksit9_6C = case_when(
      TPKSIT9_6 == 1 ~ 1,
      is.na(TPKSIT9_6) ~ 0),
    tpksit9_8C = case_when(
      TPKSIT9_8 == 1 ~ 1,
      is.na(TPKSIT9_8) ~ 0))
#Codierung des TPK-Tests.


# Subskala Situatives TPK Audio-Visuelle Technologie #####################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    tpksit4_2C = case_when(
      is.na(TPKSIT4_2) ~ 1,
      TPKSIT4_2 == 1 ~ 0),
    tpksit4_3C = case_when(
      is.na(TPKSIT4_3) ~ 1,
      TPKSIT4_3 == 1 ~ 0),
    tpksit4_5C = case_when(
      is.na(TPKSIT4_5) ~ 1,
      TPKSIT4_5 == 1 ~ 0),
    tpksit4_6C = case_when(
      is.na(TPKSIT4_6) ~ 1,
      TPKSIT4_6 == 1 ~ 0),
    tpksit4_7C = case_when(
      is.na(TPKSIT4_7) ~ 1,
      TPKSIT4_7 == 1 ~ 0),
    tpksit4_8C = case_when(
      is.na(TPKSIT4_8) ~ 1,
      TPKSIT4_8 == 1 ~ 0),
    tpksit4_1C = case_when(
      TPKSIT4_1 == 1 ~ 1,
      is.na(TPKSIT4_1) ~ 0),
    tpksit4_4C = case_when(
      TPKSIT4_4 == 1 ~ 1,
      is.na(TPKSIT4_4) ~ 0),
    
    tpksit10_2C = case_when(
      is.na(TPKSIT10_2) ~ 1,
      TPKSIT10_2 == 1 ~ 0),
    tpksit10_3C = case_when(
      is.na(TPKSIT10_3) ~ 1,
      TPKSIT10_3 == 1 ~ 0),
    tpksit10_6C = case_when(
      is.na(TPKSIT10_6) ~ 1,
      TPKSIT10_6 == 1 ~ 0),
    tpksit10_7C = case_when(
      is.na(TPKSIT10_7) ~ 1,
      TPKSIT10_7 == 1 ~ 0),
    tpksit10_8C = case_when(
      is.na(TPKSIT10_8) ~ 1,
      TPKSIT10_8 == 1 ~ 0),
    tpksit10_1C = case_when(
      TPKSIT10_1 == 1 ~ 1,
      is.na(TPKSIT10_1) ~ 0),
    tpksit10_4C = case_when(
      TPKSIT10_4 == 1 ~ 1,
      is.na(TPKSIT10_4) ~ 0),
    tpksit10_5C = case_when(
      TPKSIT10_5 == 1 ~ 1,
      is.na(TPKSIT10_5) ~ 0),
    
    tpksit11_1C = case_when(
      is.na(TPKSIT11_1) ~ 1,
      TPKSIT11_1 == 1 ~ 0),
    tpksit11_2C = case_when(
      is.na(TPKSIT11_2) ~ 1,
      TPKSIT11_2 == 1 ~ 0),
    tpksit11_3C = case_when(
      is.na(TPKSIT11_3) ~ 1,
      TPKSIT11_3 == 1 ~ 0),
    tpksit11_4C = case_when(
      is.na(TPKSIT11_4) ~ 1,
      TPKSIT11_4 == 1 ~ 0),
    tpksit11_5C = case_when(
      is.na(TPKSIT11_5) ~ 1,
      TPKSIT11_5 == 1 ~ 0),
    tpksit11_7C = case_when(
      is.na(TPKSIT11_7) ~ 1,
      TPKSIT11_7 == 1 ~ 0),
    tpksit11_6C = case_when(
      TPKSIT11_6 == 1 ~ 1,
      is.na(TPKSIT11_6) ~ 0),
    tpksit11_8C = case_when(
      TPKSIT11_8 == 1 ~ 1,
      is.na(TPKSIT11_8) ~ 0),
    
    tpksit12_2C = case_when(
      is.na(TPKSIT12_2) ~ 1,
      TPKSIT12_2 == 1 ~ 0),
    tpksit12_4C = case_when(
      is.na(TPKSIT12_4) ~ 1,
      TPKSIT12_4 == 1 ~ 0),
    tpksit12_6C = case_when(
      is.na(TPKSIT12_6) ~ 1,
      TPKSIT12_6 == 1 ~ 0),
    tpksit12_7C = case_when(
      is.na(TPKSIT12_7) ~ 1,
      TPKSIT12_7 == 1 ~ 0),
    tpksit12_1C = case_when(
      TPKSIT12_1 == 1 ~ 1,
      is.na(TPKSIT12_1) ~ 0),
    tpksit12_3C = case_when(
      TPKSIT12_3 == 1 ~ 1,
      is.na(TPKSIT12_3) ~ 0),
    tpksit12_5C = case_when(
      TPKSIT12_5 == 1 ~ 1,
      is.na(TPKSIT12_5) ~ 0),
    tpksit12_8C = case_when(
      TPKSIT12_8 == 1 ~ 1,
      is.na(TPKSIT12_8) ~ 0))

# Subskala Situatives TPK Text-Basierende Technologie #####################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    tpksit2_1C = case_when(
      is.na(TPKSIT2_1) ~ 1,
      TPKSIT2_1 == 1 ~ 0),
    tpksit2_3C = case_when(
      is.na(TPKSIT2_3) ~ 1,
      TPKSIT2_3 == 1 ~ 0),
    tpksit2_4C = case_when(
      is.na(TPKSIT2_4) ~ 1,
      TPKSIT2_4 == 1 ~ 0),
    tpksit2_7C = case_when(
      is.na(TPKSIT2_7) ~ 1,
      TPKSIT2_7 == 1 ~ 0),
    tpksit2_2C = case_when(
      TPKSIT2_2 == 1 ~ 1,
      is.na(TPKSIT2_2) ~ 0),
    tpksit2_5C = case_when(
      TPKSIT2_5 == 1 ~ 1,
      is.na(TPKSIT2_5) ~ 0),
    tpksit2_6C = case_when(
      TPKSIT2_6 == 1 ~ 1,
      is.na(TPKSIT2_6) ~ 0),
    tpksit2_8C = case_when(
      TPKSIT2_8 == 1 ~ 1,
      is.na(TPKSIT2_8) ~ 0),
    
    tpksit3_1C = case_when(
      is.na(TPKSIT3_1) ~ 1,
      TPKSIT3_1 == 1 ~ 0),
    tpksit3_4C = case_when(
      is.na(TPKSIT3_4) ~ 1,
      TPKSIT3_4 == 1 ~ 0),
    tpksit3_6C = case_when(
      is.na(TPKSIT3_6) ~ 1,
      TPKSIT3_6 == 1 ~ 0),
    tpksit3_7C = case_when(
      is.na(TPKSIT3_7) ~ 1,
      TPKSIT3_7 == 1 ~ 0),
    tpksit3_2C = case_when(
      TPKSIT3_2 == 1 ~ 1,
      is.na(TPKSIT3_2) ~ 0),
    tpksit3_3C = case_when(
      TPKSIT3_3 == 1 ~ 1,
      is.na(TPKSIT3_3) ~ 0),
    tpksit3_5C = case_when(
      TPKSIT3_5 == 1 ~ 1,
      is.na(TPKSIT3_5) ~ 0),
    tpksit3_8C = case_when(
      TPKSIT3_8 == 1 ~ 1,
      is.na(TPKSIT3_8) ~ 0),
    
    tpksit7_1C = case_when(
      is.na(TPKSIT7_1) ~ 1,
      TPKSIT7_1 == 1 ~ 0),
    tpksit7_4C = case_when(
      is.na(TPKSIT7_4) ~ 1,
      TPKSIT7_4 == 1 ~ 0),
    tpksit7_6C = case_when(
      is.na(TPKSIT7_6) ~ 1,
      TPKSIT7_6 == 1 ~ 0),
    tpksit7_7C = case_when(
      is.na(TPKSIT7_7) ~ 1,
      TPKSIT7_7 == 1 ~ 0),
    tpksit7_2C = case_when(
      TPKSIT7_2 == 1 ~ 1,
      is.na(TPKSIT7_2) ~ 0),
    tpksit7_3C = case_when(
      TPKSIT7_3 == 1 ~ 1,
      is.na(TPKSIT7_3) ~ 0),
    tpksit7_5C = case_when(
      TPKSIT7_5 == 1 ~ 1,
      is.na(TPKSIT7_5) ~ 0),
    tpksit7_8C = case_when(
      TPKSIT7_8 == 1 ~ 1,
      is.na(TPKSIT7_8) ~ 0))

# Subskala Situatives TPK Adaptive-Assessment Technologie #####################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    tpksit5_4C = case_when(
      is.na(TPKSIT5_4) ~ 1,
      TPKSIT5_4 == 1 ~ 0),
    tpksit5_5C = case_when(
      is.na(TPKSIT5_5) ~ 1,
      TPKSIT5_5 == 1 ~ 0),
    tpksit5_6C = case_when(
      is.na(TPKSIT5_6) ~ 1,
      TPKSIT5_6 == 1 ~ 0),
    tpksit5_7C = case_when(
      is.na(TPKSIT5_7) ~ 1,
      TPKSIT5_7 == 1 ~ 0),
    tpksit5_1C = case_when(
      TPKSIT5_1 == 1 ~ 1,
      is.na(TPKSIT5_1) ~ 0),
    tpksit5_2C = case_when(
      TPKSIT5_2 == 1 ~ 1,
      is.na(TPKSIT5_2) ~ 0),
    tpksit5_3C = case_when(
      TPKSIT5_3 == 1 ~ 1,
      is.na(TPKSIT5_3) ~ 0),
    tpksit5_8C = case_when(
      TPKSIT5_8 == 1 ~ 1,
      is.na(TPKSIT5_8) ~ 0),
    
    tpksit6_1C = case_when(
      is.na(TPKSIT6_1) ~ 1,
      TPKSIT6_1 == 1 ~ 0),
    tpksit6_6C = case_when(
      is.na(TPKSIT6_6) ~ 1,
      TPKSIT6_6 == 1 ~ 0),
    tpksit6_7C = case_when(
      is.na(TPKSIT6_7) ~ 1,
      TPKSIT6_7 == 1 ~ 0),
    tpksit6_8C = case_when(
      is.na(TPKSIT6_8) ~ 1,
      TPKSIT6_8 == 1 ~ 0),
    tpksit6_2C = case_when(
      TPKSIT6_2 == 1 ~ 1,
      is.na(TPKSIT6_2) ~ 0),
    tpksit6_3C = case_when(
      TPKSIT6_3 == 1 ~ 1,
      is.na(TPKSIT6_3) ~ 0),
    tpksit6_4C = case_when(
      TPKSIT6_4 == 1 ~ 1,
      is.na(TPKSIT6_4) ~ 0),
    tpksit6_5C = case_when(
      TPKSIT6_5 == 1 ~ 1,
      is.na(TPKSIT6_5) ~ 0),
    
    tpksit8_2C = case_when(
      is.na(TPKSIT8_2) ~ 1,
      TPKSIT8_2 == 1 ~ 0),
    tpksit8_4C = case_when(
      is.na(TPKSIT8_4) ~ 1,
      TPKSIT8_4 == 1 ~ 0),
    tpksit8_5C = case_when(
      is.na(TPKSIT8_5) ~ 1,
      TPKSIT8_5 == 1 ~ 0),
    tpksit8_6C = case_when(
      is.na(TPKSIT8_6) ~ 1,
      TPKSIT8_6 == 1 ~ 0),
    tpksit8_8C = case_when(
      is.na(TPKSIT8_8) ~ 1,
      TPKSIT8_8 == 1 ~ 0),
    tpksit8_1C = case_when(
      TPKSIT8_1 == 1 ~ 1,
      is.na(TPKSIT8_1) ~ 0),
    tpksit8_3C = case_when(
      TPKSIT8_3 == 1 ~ 1,
      is.na(TPKSIT8_3) ~ 0),
    tpksit8_7C = case_when(
      TPKSIT8_7 == 1 ~ 1,
      is.na(TPKSIT8_7) ~ 0))

# Subskala Konzeptuelles TPK Potentiale #####################
LAA_K4_MZP1 <- LAA_K4_MZP1 |>
  mutate(
    tpkpot1_1C = case_when(
      is.na(TPKPOT1_1) ~ 1,
      TPKPOT1_1 == 1 ~ 0),
    tpkpot1_3C = case_when(
      is.na(TPKPOT1_3) ~ 1,
      TPKPOT1_3 == 1 ~ 0),
    tpkpot1_2C = case_when(
      TPKPOT1_2 == 1 ~ 1,
      is.na(TPKPOT1_2) ~ 0),
    tpkpot1_4C = case_when(
      TPKPOT1_4 == 1 ~ 1,
      is.na(TPKPOT1_4) ~ 0),
    
    tpkpot2_2C = case_when(
      is.na(TPKPOT2_2) ~ 1,
      TPKPOT2_2 == 1 ~ 0),
    tpkpot2_1C = case_when(
      TPKPOT2_1 == 1 ~ 1,
      is.na(TPKPOT2_1) ~ 0),
    tpkpot2_3C = case_when(
      TPKPOT2_3 == 1 ~ 1,
      is.na(TPKPOT2_3) ~ 0),
    tpkpot2_4C = case_when(
      TPKPOT2_4 == 1 ~ 1,
      is.na(TPKPOT2_4) ~ 0),
    
    tpkpot3_1C = case_when(
      is.na(TPKPOT3_1) ~ 1,
      TPKPOT3_1 == 1 ~ 0),
    tpkpot3_3C = case_when(
      is.na(TPKPOT3_3) ~ 1,
      TPKPOT3_3 == 1 ~ 0),
    tpkpot3_2C = case_when(
      TPKPOT3_2 == 1 ~ 1,
      is.na(TPKPOT3_2) ~ 0),
    tpkpot3_4C = case_when(
      TPKPOT3_4 == 1 ~ 1,
      is.na(TPKPOT3_4) ~ 0),
    
    tpkpot4_3C = case_when(
      is.na(TPKPOT4_3) ~ 1,
      TPKPOT4_3 == 1 ~ 0),
    tpkpot4_4C = case_when(
      is.na(TPKPOT4_4) ~ 1,
      TPKPOT4_4 == 1 ~ 0),
    tpkpot4_1C = case_when(
      TPKPOT4_1 == 1 ~ 1,
      is.na(TPKPOT4_1) ~ 0),
    tpkpot4_2C = case_when(
      TPKPOT4_2 == 1 ~ 1,
      is.na(TPKPOT4_2) ~ 0),
    
    tpkpot5_1C = case_when(
      is.na(TPKPOT5_1) ~ 1,
      TPKPOT5_1 == 1 ~ 0),
    tpkpot5_4C = case_when(
      is.na(TPKPOT5_4) ~ 1,
      TPKPOT5_4 == 1 ~ 0),
    tpkpot5_2C = case_when(
      TPKPOT5_2 == 1 ~ 1,
      is.na(TPKPOT5_2) ~ 0),
    tpkpot5_3C = case_when(
      TPKPOT5_3 == 1 ~ 1,
      is.na(TPKPOT5_3) ~ 0))

# Subskala Konzeptuelles TPK Prinzipien #####################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    tpksup1_1C = case_when(
      is.na(TPKSUP1_1) ~ 1,
      TPKSUP1_1 == 1 ~ 0),
    tpksup1_3C = case_when(
      is.na(TPKSUP1_3) ~ 1,
      TPKSUP1_3 == 1 ~ 0),
    tpksup1_4C = case_when(
      is.na(TPKSUP1_4) ~ 1,
      TPKSUP1_4 == 1 ~ 0),
    tpksup1_2C = case_when(
      TPKSUP1_2 == 1 ~ 1,
      is.na(TPKSUP1_2) ~ 0),
    
    tpksup2_3C = case_when(
      is.na(TPKSUP2_3) ~ 1,
      TPKSUP2_3 == 1 ~ 0),
    tpksup2_4C = case_when(
      is.na(TPKSUP2_4) ~ 1,
      TPKSUP2_4 == 1 ~ 0),
    tpksup2_1C = case_when(
      TPKSUP2_1 == 1 ~ 1,
      is.na(TPKSUP2_1) ~ 0),
    tpksup2_2C = case_when(
      TPKSUP2_2 == 1 ~ 1,
      is.na(TPKSUP2_2) ~ 0),
    
    tpksup3_1C = case_when(
      is.na(TPKSUP3_1) ~ 1,
      TPKSUP3_1 == 1 ~ 0),
    tpksup3_3C = case_when(
      is.na(TPKSUP3_3) ~ 1,
      TPKSUP3_3 == 1 ~ 0),
    tpksup3_2C = case_when(
      TPKSUP3_2 == 1 ~ 1,
      is.na(TPKSUP3_2) ~ 0),
    tpksup3_4C = case_when(
      TPKSUP3_4 == 1 ~ 1,
      is.na(TPKSUP3_4) ~ 0))


#### Skript 11b TPK_Test Auswertung #########################
LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    #Berechnung der Scores für die Subskalen & die Gesamtskala des situationalen TPK.
    tpksit_score_av = (tpksit4_1C + tpksit4_2C + tpksit4_3C + tpksit4_4C + tpksit4_5C + 
                       tpksit4_6C + tpksit4_7C + tpksit4_8C + tpksit10_1C +
                       tpksit10_2C + tpksit10_3C + tpksit10_4C + tpksit10_5C + 
                       tpksit10_6C + tpksit10_7C + tpksit10_8C + tpksit11_1C +
                       tpksit11_2C + tpksit11_3C + tpksit11_4C + tpksit11_5C + 
                       tpksit11_6C + tpksit11_7C + tpksit11_8C + tpksit12_1C +
                       tpksit12_2C + tpksit12_3C + tpksit12_4C + tpksit12_5C + 
                       tpksit12_6C + tpksit12_7C + tpksit12_8C) / 32 *100,
    
    tpksit_score_tb = (tpksit2_1C + tpksit2_2C + tpksit2_3C + tpksit2_4C + 
                       tpksit2_5C + tpksit2_6C + tpksit2_7C + tpksit2_8C + 
                       tpksit3_1C + tpksit3_2C + tpksit3_3C + tpksit3_4C + 
                       tpksit3_5C + tpksit3_6C + tpksit3_7C + tpksit3_8C + 
                       tpksit7_1C + tpksit7_2C + tpksit7_3C + tpksit7_4C + 
                       tpksit7_5C + tpksit7_6C + tpksit7_7C + tpksit7_8C) /24 *100,
    
    tpksit_score_aa = (tpksit5_1C + tpksit5_2C + tpksit5_3C + tpksit5_4C + 
                       tpksit5_5C + tpksit5_6C + tpksit5_7C + tpksit5_8C + 
                       tpksit6_1C + tpksit6_2C + tpksit6_3C + tpksit6_4C + 
                       tpksit6_5C + tpksit6_6C + tpksit6_7C + tpksit6_8C + 
                       tpksit8_1C + tpksit8_2C + tpksit8_3C + tpksit8_4C + 
                       tpksit8_5C + tpksit8_6C + tpksit8_7C + tpksit8_8C) /24 *100,
    
    tpksit_score = (tpksit2_1C + tpksit2_2C + tpksit2_3C + tpksit2_4C + 
                    tpksit2_5C + tpksit2_6C + tpksit2_7C + tpksit2_8C + 
                    tpksit3_1C + tpksit3_2C + tpksit3_3C + tpksit3_4C + 
                    tpksit3_5C + tpksit3_6C + tpksit3_7C + tpksit3_8C + 
                    tpksit4_1C + tpksit4_2C + tpksit4_3C + tpksit4_4C + 
                    tpksit4_5C + tpksit4_6C + tpksit4_7C + tpksit4_8C + 
                    tpksit5_1C + tpksit5_2C + tpksit5_3C + tpksit5_4C + 
                    tpksit5_5C + tpksit5_6C + tpksit5_7C + tpksit5_8C + 
                    tpksit6_1C + tpksit6_2C + tpksit6_3C + tpksit6_4C + 
                    tpksit6_5C + tpksit6_6C + tpksit6_7C + tpksit6_8C + 
                    tpksit7_1C + tpksit7_2C + tpksit7_3C + tpksit7_4C + 
                    tpksit7_5C + tpksit7_6C + tpksit7_7C + tpksit7_8C + 
                    tpksit8_1C + tpksit8_2C + tpksit8_3C + tpksit8_4C + 
                    tpksit8_5C + tpksit8_6C + tpksit8_7C + tpksit8_8C + 
                    tpksit10_1C + tpksit10_2C + tpksit10_3C + tpksit10_4C + 
                    tpksit10_5C + tpksit10_6C + tpksit10_7C + tpksit10_8C + 
                    tpksit11_1C + tpksit11_2C + tpksit11_3C + tpksit11_4C + 
                    tpksit11_5C + tpksit11_6C + tpksit11_7C + tpksit11_8C + 
                    tpksit12_1C + tpksit12_2C + tpksit12_3C + tpksit12_4C + 
                    tpksit12_5C + tpksit12_6C + tpksit12_7C + tpksit12_8C) /80 *100)

LAA_K4_MZP1 <- LAA_K4_MZP1 |> 
  mutate(
    #Berechnung der Scores für Subskalen & die Gesamtskala des konzeptuellen TPK.
    tpkpot_score = (tpkpot1_1C + tpkpot1_2C + tpkpot1_3C + tpkpot1_4C + 
                    tpkpot2_1C + tpkpot2_2C + tpkpot2_3C + tpkpot2_4C + 
                    tpkpot3_1C + tpkpot3_2C + tpkpot3_3C + tpkpot3_4C + 
                    tpkpot4_1C + tpkpot4_2C + tpkpot4_3C + tpkpot4_4C + 
                    tpkpot5_1C + tpkpot5_2C + tpkpot5_3C + tpkpot5_4C) /20 *100,
    
    tpksup_score = (tpksup1_1C + tpksup1_2C + tpksup1_3C + tpksup1_4C + 
                    tpksup2_1C + tpksup2_2C + tpksup2_3C + tpksup2_4C +
                    tpksup3_1C + tpksup3_2C + tpksup3_3C + tpksup3_4C) /12 *100,
    
    tpkcon_score = (tpkpot1_1C + tpkpot1_2C + tpkpot1_3C + tpkpot1_4C + 
                    tpkpot2_1C + tpkpot2_2C + tpkpot2_3C + tpkpot2_4C + 
                    tpkpot3_1C + tpkpot3_2C + tpkpot3_3C + tpkpot3_4C + 
                    tpkpot4_1C + tpkpot4_2C + tpkpot4_3C + tpkpot4_4C + 
                    tpkpot5_1C + tpkpot5_2C + tpkpot5_3C + tpkpot5_4C +
                    tpksup1_1C + tpksup1_2C + tpksup1_3C + tpksup1_4C + 
                    tpksup2_1C + tpksup2_2C + tpksup2_3C + tpksup2_4C +
                    tpksup3_1C + tpksup3_2C + tpksup3_3C + tpksup3_4C) /32 *100)
```


```{r}
############################################################################## #
##### BILDUNG EINES SCORES JE ITEM                                          ####
############################################################################## #

## LAA ####################################################################### #

LAA_K4_MZP1 <- LAA_K4_MZP1 %>%
  mutate(
        # tpksit1 = rowMeans(data.frame(tpksit1_1C, tpksit1_2C, 
        #                                tpksit1_3C, tpksit1_4C, 
        #                                tpksit1_5C, tpksit1_6C, 
        #                                tpksit1_7C, tpksit1_8C),
        #                     na.rm = T),
         tpksit2 = rowMeans(data.frame(tpksit2_1C, tpksit2_2C, 
                                       tpksit2_3C, tpksit2_4C, 
                                       tpksit2_5C, tpksit2_6C, 
                                       tpksit2_7C, tpksit2_8C),
                            na.rm = T),
         tpksit3 = rowMeans(data.frame(tpksit3_1C, tpksit3_2C, 
                                       tpksit3_3C, tpksit3_4C, 
                                       tpksit3_5C, tpksit3_6C, 
                                       tpksit3_7C, tpksit3_8C),
                            na.rm = T),
         tpksit4 = rowMeans(data.frame(tpksit4_1C, tpksit4_2C, 
                                       tpksit4_3C, tpksit4_4C, 
                                       tpksit4_5C, tpksit4_6C, 
                                       tpksit4_7C, tpksit4_8C),
                            na.rm = T),
         tpksit5 = rowMeans(data.frame(tpksit5_1C, tpksit5_2C, 
                                       tpksit5_3C, tpksit5_4C, 
                                       tpksit5_5C, tpksit5_6C, 
                                       tpksit5_7C, tpksit5_8C),
                            na.rm = T),
         tpksit6 = rowMeans(data.frame(tpksit6_1C, tpksit6_2C, 
                                       tpksit6_3C, tpksit6_4C, 
                                       tpksit6_5C, tpksit6_6C, 
                                       tpksit6_7C, tpksit6_8C),
                            na.rm = T),
         tpksit7 = rowMeans(data.frame(tpksit7_1C, tpksit7_2C, 
                                       tpksit7_3C, tpksit7_4C, 
                                       tpksit7_5C, tpksit7_6C, 
                                       tpksit7_7C, tpksit7_8C),
                            na.rm = T),
         tpksit8 = rowMeans(data.frame(tpksit8_1C, tpksit8_2C, 
                                       tpksit8_3C, tpksit8_4C, 
                                       tpksit8_5C, tpksit8_6C, 
                                       tpksit8_7C, tpksit8_8C),
                            na.rm = T),
         tpksit10 = rowMeans(data.frame(tpksit10_1C, tpksit10_2C, 
                                        tpksit10_3C, tpksit10_4C, 
                                        tpksit10_5C, tpksit10_6C, 
                                        tpksit10_7C, tpksit10_8C),
                            na.rm = T),
         tpksit11 = rowMeans(data.frame(tpksit11_1C, tpksit11_2C, 
                                        tpksit11_3C, tpksit11_4C, 
                                        tpksit11_5C, tpksit11_6C, 
                                        tpksit11_7C, tpksit11_8C),
                            na.rm = T),
         tpksit12 = rowMeans(data.frame(tpksit12_1C, tpksit12_2C, 
                                        tpksit12_3C, tpksit12_4C, 
                                        tpksit12_5C, tpksit12_6C, 
                                        tpksit12_7C, tpksit12_8C),
                            na.rm = T),
         tpkpot1 = rowMeans(data.frame(tpkpot1_1C, tpkpot1_2C, 
                                       tpkpot1_3C, tpkpot1_4C ),
                            na.rm = T),
         tpkpot2 = rowMeans(data.frame(tpkpot2_1C, tpkpot2_2C, 
                                        tpkpot2_3C, tpkpot2_4C ),
                            na.rm = T),
         tpkpot3 = rowMeans(data.frame(tpkpot3_1C, tpkpot3_2C, 
                                        tpkpot3_3C, tpkpot3_4C),
                            na.rm = T),
         tpkpot4 = rowMeans(data.frame(tpkpot4_1C, tpkpot4_2C, 
                                        tpkpot4_3C, tpkpot4_4C),
                            na.rm = T),
         tpkpot5 = rowMeans(data.frame(tpkpot5_1C, tpkpot5_2C, 
                                        tpkpot5_3C, tpkpot5_4C),
                            na.rm = T),
         tpksup1 = rowMeans(data.frame(tpksup1_1C, tpksup1_2C, 
                                        tpksup1_3C, tpksup1_4C),
                            na.rm = T),
         tpksup2 = rowMeans(data.frame(tpksup2_1C, tpksup2_2C, 
                                        tpksup2_3C, tpksup2_4C),
                            na.rm = T),
         tpksup3 = rowMeans(data.frame(tpksup3_1C, tpksup3_2C, 
                                        tpksup3_3C, tpksup3_4C),
                            na.rm = T))



## ALK ####################################################################### #

ALK_K4_MZP1 <- ALK_K4_MZP1 %>%
  mutate(tpksit2 = rowMeans(data.frame(tpksit2_1c_01K4, tpksit2_2c_01K4, 
                                       tpksit2_3c_01K4, tpksit2_4c_01K4, 
                                       tpksit2_5c_01K4, tpksit2_6c_01K4, 
                                       tpksit2_7c_01K4, tpksit2_8c_01K4),
                            na.rm = T),
         tpksit3 = rowMeans(data.frame(tpksit3_1c_01K4, tpksit3_2c_01K4, 
                                       tpksit3_3c_01K4, tpksit3_4c_01K4, 
                                       tpksit3_5c_01K4, tpksit3_6c_01K4, 
                                       tpksit3_7c_01K4, tpksit3_8c_01K4),
                            na.rm = T),
         tpksit4 = rowMeans(data.frame(tpksit4_1c_01K4, tpksit4_2c_01K4, 
                                       tpksit4_3c_01K4, tpksit4_4c_01K4, 
                                       tpksit4_5c_01K4, tpksit4_6c_01K4, 
                                       tpksit4_7c_01K4, tpksit4_8c_01K4),
                            na.rm = T),
         tpksit5 = rowMeans(data.frame(tpksit5_1c_01K4, tpksit5_2c_01K4, 
                                       tpksit5_3c_01K4, tpksit5_4c_01K4, 
                                       tpksit5_5c_01K4, tpksit5_6c_01K4, 
                                       tpksit5_7c_01K4, tpksit5_8c_01K4),
                            na.rm = T),
         tpksit6 = rowMeans(data.frame(tpksit6_1c_01K4, tpksit6_2c_01K4, 
                                       tpksit6_3c_01K4, tpksit6_4c_01K4, 
                                       tpksit6_5c_01K4, tpksit6_6c_01K4, 
                                       tpksit6_7c_01K4, tpksit6_8c_01K4),
                            na.rm = T),
         tpksit7 = rowMeans(data.frame(tpksit7_1c_01K4, tpksit7_2c_01K4, 
                                       tpksit7_3c_01K4, tpksit7_4c_01K4, 
                                       tpksit7_5c_01K4, tpksit7_6c_01K4, 
                                       tpksit7_7c_01K4, tpksit7_8c_01K4),
                            na.rm = T),
         tpksit8 = rowMeans(data.frame(tpksit8_1c_01K4, tpksit8_2c_01K4, 
                                       tpksit8_3c_01K4, tpksit8_4c_01K4, 
                                       tpksit8_5c_01K4, tpksit8_6c_01K4, 
                                       tpksit8_7c_01K4, tpksit8_8c_01K4),
                            na.rm = T),
         tpksit10 = rowMeans(data.frame(tpksit10_1c_01K4, tpksit10_2c_01K4, 
                                        tpksit10_3c_01K4, tpksit10_4c_01K4, 
                                        tpksit10_5c_01K4, tpksit10_6c_01K4, 
                                        tpksit10_7c_01K4, tpksit10_8c_01K4),
                            na.rm = T),
         tpksit11 = rowMeans(data.frame(tpksit11_1c_01K4, tpksit11_2c_01K4, 
                                        tpksit11_3c_01K4, tpksit11_4c_01K4, 
                                        tpksit11_5c_01K4, tpksit11_6c_01K4, 
                                        tpksit11_7c_01K4, tpksit11_8c_01K4),
                            na.rm = T),
         tpksit12 = rowMeans(data.frame(tpksit12_1c_01K4, tpksit12_2c_01K4, 
                                        tpksit12_3c_01K4, tpksit12_4c_01K4, 
                                        tpksit12_5c_01K4, tpksit12_6c_01K4, 
                                        tpksit12_7c_01K4, tpksit12_8c_01K4),
                            na.rm = T),
         tpkpot1 = rowMeans(data.frame(tpkpot1_1c_01K4, tpkpot1_2c_01K4, 
                                       tpkpot1_3c_01K4, tpkpot1_4c_01K4 ),
                            na.rm = T),
         tpkpot2 = rowMeans(data.frame(tpkpot2_1c_01K4, tpkpot2_2c_01K4, 
                                        tpkpot2_3c_01K4, tpkpot2_4c_01K4 ),
                            na.rm = T),
         tpkpot3 = rowMeans(data.frame(tpkpot3_1c_01K4, tpkpot3_2c_01K4, 
                                        tpkpot3_3c_01K4, tpkpot3_4c_01K4),
                            na.rm = T),
         tpkpot4 = rowMeans(data.frame(tpkpot4_1c_01K4, tpkpot4_2c_01K4, 
                                        tpkpot4_3c_01K4, tpkpot4_4c_01K4),
                            na.rm = T),
         tpkpot5 = rowMeans(data.frame(tpkpot5_1c_01K4, tpkpot5_2c_01K4, 
                                        tpkpot5_3c_01K4, tpkpot5_4c_01K4),
                            na.rm = T),
         tpksup1 = rowMeans(data.frame(tpksup1_1c_01K4, tpksup1_2c_01K4, 
                                        tpksup1_3c_01K4, tpksup1_4c_01K4),
                            na.rm = T),
         tpksup2 = rowMeans(data.frame(tpksup2_1c_01K4, tpksup2_2c_01K4, 
                                        tpksup2_3c_01K4, tpksup2_4c_01K4),
                            na.rm = T),
         tpksup3 = rowMeans(data.frame(tpksup3_1c_01K4, tpksup3_2c_01K4, 
                                        tpksup3_3c_01K4, tpksup3_4c_01K4),
                            na.rm = T))


## SAB ####################################################################### #

SAB_K4_MZP1 <- SAB_K4_MZP1 %>%
  mutate(tpksit2 = rowMeans(data.frame(tpksit2_1c_01K4, tpksit2_2c_01K4, 
                                       tpksit2_3c_01K4, tpksit2_4c_01K4, 
                                       tpksit2_5c_01K4, tpksit2_6c_01K4, 
                                       tpksit2_7c_01K4, tpksit2_8c_01K4),
                            na.rm = T),
         tpksit3 = rowMeans(data.frame(tpksit3_1c_01K4, tpksit3_2c_01K4, 
                                       tpksit3_3c_01K4, tpksit3_4c_01K4, 
                                       tpksit3_5c_01K4, tpksit3_6c_01K4, 
                                       tpksit3_7c_01K4, tpksit3_8c_01K4),
                            na.rm = T),
         tpksit4 = rowMeans(data.frame(tpksit4_1c_01K4, tpksit4_2c_01K4, 
                                       tpksit4_3c_01K4, tpksit4_4c_01K4, 
                                       tpksit4_5c_01K4, tpksit4_6c_01K4, 
                                       tpksit4_7c_01K4, tpksit4_8c_01K4),
                            na.rm = T),
         tpksit5 = rowMeans(data.frame(tpksit5_1c_01K4, tpksit5_2c_01K4, 
                                       tpksit5_3c_01K4, tpksit5_4c_01K4, 
                                       tpksit5_5c_01K4, tpksit5_6c_01K4, 
                                       tpksit5_7c_01K4, tpksit5_8c_01K4),
                            na.rm = T),
         tpksit6 = rowMeans(data.frame(tpksit6_1c_01K4, tpksit6_2c_01K4, 
                                       tpksit6_3c_01K4, tpksit6_4c_01K4, 
                                       tpksit6_5c_01K4, tpksit6_6c_01K4, 
                                       tpksit6_7c_01K4, tpksit6_8c_01K4),
                            na.rm = T),
         tpksit7 = rowMeans(data.frame(tpksit7_1c_01K4, tpksit7_2c_01K4, 
                                       tpksit7_3c_01K4, tpksit7_4c_01K4, 
                                       tpksit7_5c_01K4, tpksit7_6c_01K4, 
                                       tpksit7_7c_01K4, tpksit7_8c_01K4),
                            na.rm = T),
         tpksit8 = rowMeans(data.frame(tpksit8_1c_01K4, tpksit8_2c_01K4, 
                                       tpksit8_3c_01K4, tpksit8_4c_01K4, 
                                       tpksit8_5c_01K4, tpksit8_6c_01K4, 
                                       tpksit8_7c_01K4, tpksit8_8c_01K4),
                            na.rm = T),
         tpksit10 = rowMeans(data.frame(tpksit10_1c_01K4, tpksit10_2c_01K4, 
                                        tpksit10_3c_01K4, tpksit10_4c_01K4, 
                                        tpksit10_5c_01K4, tpksit10_6c_01K4, 
                                        tpksit10_7c_01K4, tpksit10_8c_01K4),
                            na.rm = T),
         tpksit11 = rowMeans(data.frame(tpksit11_1c_01K4, tpksit11_2c_01K4, 
                                        tpksit11_3c_01K4, tpksit11_4c_01K4, 
                                        tpksit11_5c_01K4, tpksit11_6c_01K4, 
                                        tpksit11_7c_01K4, tpksit11_8c_01K4),
                            na.rm = T),
         tpksit12 = rowMeans(data.frame(tpksit12_1c_01K4, tpksit12_2c_01K4, 
                                        tpksit12_3c_01K4, tpksit12_4c_01K4, 
                                        tpksit12_5c_01K4, tpksit12_6c_01K4, 
                                        tpksit12_7c_01K4, tpksit12_8c_01K4),
                            na.rm = T),
         tpkpot1 = rowMeans(data.frame(tpkpot1_1c_01K4, tpkpot1_2c_01K4, 
                                       tpkpot1_3c_01K4, tpkpot1_4c_01K4 ),
                            na.rm = T),
         tpkpot2 = rowMeans(data.frame(tpkpot2_1c_01K4, tpkpot2_2c_01K4, 
                                        tpkpot2_3c_01K4, tpkpot2_4c_01K4 ),
                            na.rm = T),
         tpkpot3 = rowMeans(data.frame(tpkpot3_1c_01K4, tpkpot3_2c_01K4, 
                                        tpkpot3_3c_01K4, tpkpot3_4c_01K4),
                            na.rm = T),
         tpkpot4 = rowMeans(data.frame(tpkpot4_1c_01K4, tpkpot4_2c_01K4, 
                                        tpkpot4_3c_01K4, tpkpot4_4c_01K4),
                            na.rm = T),
         tpkpot5 = rowMeans(data.frame(tpkpot5_1c_01K4, tpkpot5_2c_01K4, 
                                        tpkpot5_3c_01K4, tpkpot5_4c_01K4),
                            na.rm = T),
         tpksup1 = rowMeans(data.frame(tpksup1_1c_01K4, tpksup1_2c_01K4, 
                                        tpksup1_3c_01K4, tpksup1_4c_01K4),
                            na.rm = T),
         tpksup2 = rowMeans(data.frame(tpksup2_1c_01K4, tpksup2_2c_01K4, 
                                        tpksup2_3c_01K4, tpksup2_4c_01K4),
                            na.rm = T),
         tpksup3 = rowMeans(data.frame(tpksup3_1c_01K4, tpksup3_2c_01K4, 
                                        tpksup3_3c_01K4, tpksup3_4c_01K4),
                            na.rm = T))
```

# Sit-Factor

::: panel-tabset

## Reliability

```{r}
psych::omega(LAA_K4_MZP1%>%dplyr::select(tpksit2:tpksit12), nfactors = 3)
```

> Reliability is not good.

```{r}
# Omega without the subscale AV
psych::omega(LAA_K4_MZP1%>%dplyr::select(tpksit2,
                                         tpksit3,
                                         #tpksit4,
                                         tpksit5,
                                         tpksit6,
                                         tpksit7,
                                         tpksit8#,
                                         #tpksit10,
                                         #tpksit11,
                                         #tpksit12
                                 ), nfactors = 2)
```

> And can't be improved by deleting, e.g. a subscale.


## CFAs


```{r}
model <- '
          tpk_sit =~ tpksit2 +
                     tpksit3 +
                     tpksit4 +
                     tpksit5 +
                     tpksit6 +
                     tpksit7 +
                     tpksit8 +
                     tpksit10 +
                     tpksit11 +
                     tpksit12
         '

fit <- lavaan::cfa(model, LAA_K4_MZP1)
summary(fit, fit.measures = TRUE)
```

CFA shows not-so-good fit. But can be greatly improved by deleting the subscale AV.

```{r}
model <- '
          tpk_sit =~ tpksit2 +
                     tpksit3 +
                     #tpksit4 +
                     tpksit5 +
                     tpksit6 +
                     tpksit7 +
                     tpksit8 #+
                     #tpksit10 +
                     #tpksit11 +
                     #tpksit12
         '

fit <- lavaan::cfa(model, LAA_K4_MZP1)
summary(fit, fit.measures = TRUE)
```


## ALK

Same works with ALK, there, also the reliability is improved.

```{r}
psych::omega(ALK_K4_MZP1%>%dplyr::select(tpksit2:tpksit12), nfactors = 3)
```
Reliability is meh.  

Weakest items are `tpksit4`, `tpksit10` and , `tpksit11`. They are all from the subscale AV. If we delete one more item (`tpksit12`) we could delete the entire subscale.  


```{r}
# Omega without the subscale AV
psych::omega(ALK_K4_MZP1%>%dplyr::select(tpksit2,
                                 tpksit3,
                                 #tpksit4,
                                 tpksit5,
                                 tpksit6,
                                 tpksit7,
                                 tpksit8#,
                                 #tpksit10,
                                 #tpksit11,
                                 #tpksit12
                                 ), nfactors = 2)
```


```{r}
model <- '
          tpk_sit =~ tpksit2 +
                     tpksit3 +
                     #tpksit4 +
                     tpksit5 +
                     tpksit6 +
                     tpksit7 +
                     tpksit8 #+
                     #tpksit10 +
                     #tpksit11 +
                     #tpksit12
         '

fit <- lavaan::cfa(model, ALK_K4_MZP1)
summary(fit, fit.measures = TRUE)
```

## SAB

Same works with SAB, there, also the reliability is improved.

```{r}
psych::omega(SAB_K4_MZP1%>%dplyr::select(tpksit2:tpksit12), nfactors = 3)
```
Reliability is meh.  

If we delete the subscale AV: 


```{r}
# Omega without the subscale AV
psych::omega(SAB_K4_MZP1%>%dplyr::select(tpksit2,
                                 tpksit3,
                                 #tpksit4,
                                 tpksit5,
                                 tpksit6,
                                 tpksit7,
                                 tpksit8#,
                                 #tpksit10,
                                 #tpksit11,
                                 #tpksit12
                                 ), nfactors = 2)
```

\

This model also delivers good fit.

```{r}
model <- '
          tpk_sit =~ tpksit2 +
                     tpksit3 +
                     #tpksit4 +
                     tpksit5 +
                     tpksit6 +
                     tpksit7 +
                     tpksit8 #+
                     #tpksit10 +
                     #tpksit11 +
                     #tpksit12
         '

fit <- lavaan::cfa(model, SAB_K4_MZP1)
summary(fit, fit.measures = TRUE)
```


## My recommendation

(from a statistical point of view)

* Note: Maybe the measurement models are not equal over the groups?
* We can improve fit greatly, when deleting the subscale AV
* We should first check if there are Items that seem "old" and check if deleting them would improve reliability and fit
  - I feel like the only item building on "dated" concepts is item 1, which isn't part of any scale anyway

:::







# Con-Factor

::: panel-tabset

## Reliability

```{r}
psych::omega(LAA_K4_MZP1%>%dplyr::select(tpkpot1:tpksup3), nfactors = 2)
```

> Reliability is not good.

```{r}
# Omega without the subscale AV
psych::omega(LAA_K4_MZP1%>%dplyr::select(tpkpot1,
                                         tpkpot2,
                                         tpkpot3,
                                         #tpkpot4,
                                         tpkpot5#,
                                         # tpksup1,
                                         #tpksup2#,
                                         # tpksup3
                                 ), nfactors = 1)
```

> And can't be improved by deleting, e.g. a subscale.


## CFAs


```{r}
model <- '
          tpk_con =~ tpkpot1 +
                     tpkpot2 +
                     tpkpot3 +
                     tpkpot4 +
                     tpkpot5 +
                     tpksup1 +
                     tpksup2 +
                     tpksup3
         '

fit <- lavaan::cfa(model, LAA_K4_MZP1)
summary(fit, fit.measures = TRUE)
```

CFA shows fit concerning CFI and TLI is not good. But can be greatly improved by deleting the subscale `sup` and item `tpkpot4` from the `pot` subscale.

```{r}
model <- '
          tpk_con =~ tpkpot1 +
                     tpkpot2 +
                     tpkpot3 +
                     #tpkpot4 +
                     tpkpot5 #+
                     #tpksup1 +
                     #tpksup2 +
                     #tpksup3
         '

fit <- lavaan::cfa(model, LAA_K4_MZP1)
summary(fit, fit.measures = TRUE)
```


## ALK

Same works with ALK, there, also the reliability is improved.

```{r}
psych::omega(ALK_K4_MZP1%>%dplyr::select(tpkpot1:tpksup3), nfactors = 2)
```
Reliability is very bad.  

Can be improved, deleting the subscale `sup` and item `tpkpot4` from the `pot` subscale.


```{r}
# Omega without the subscale AV
psych::omega(ALK_K4_MZP1%>%dplyr::select(tpkpot1,
                                         tpkpot2,
                                         tpkpot3,
                                         #tpkpot4,
                                         tpkpot5#,
                                         #tpksup1,
                                         #tpksup2,
                                         #tpksup3
                                 ), nfactors = 1)
```

\

This model also delivers good fit.

```{r}
model <- '
          tpk_con =~ tpkpot1 +
                     tpkpot2 +
                     tpkpot3 +
                     #tpkpot4 +
                     tpkpot5 #+
                     #tpksup1 +
                     #tpksup2 +
                     #tpksup3
         '

fit <- lavaan::cfa(model, ALK_K4_MZP1)
summary(fit, fit.measures = TRUE)
```

## SAB

Same works with SAB, there, also the reliability is improved.

```{r}
psych::omega(SAB_K4_MZP1%>%dplyr::select(tpkpot1:tpksup3), nfactors = 2)
```
Reliability is meh.  

Can **not** be improved, deleting the subscale `sup` and item `tpkpot4` from the `pot` subscale.


```{r}
# Omega without the subscale AV
psych::omega(SAB_K4_MZP1%>%dplyr::select(tpkpot1,
                                         tpkpot2,
                                         tpkpot3,
                                         #tpkpot4,
                                         tpkpot5#,
                                         #tpksup1,
                                         #tpksup2,
                                         #tpksup3
                                 ), nfactors = 1)
```

\

This model also delivers good fit.

```{r}
model <- '
          tpk_con =~ tpkpot1 +
                     tpkpot2 +
                     tpkpot3 +
                     # tpkpot4 +
                     tpkpot5 #+
                     # tpksup1 +
                     # tpksup2 +
                     # tpksup3
         '

fit <- lavaan::cfa(model, SAB_K4_MZP1)
summary(fit, fit.measures = TRUE)
```


## My recommendation

(from a statistical point of view)

* Note: Maybe the measurement models are not equal over the groups?
* We can improve fit greatly, when deleting the subscale `sub` and item `tpkpot4` from subscale `pot`
* We should first check if there are Items that seem "old" and check if deleting them would improve reliability and fit
  - ...

:::



# Computational environment

## Packages

```{r}
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```

## R Version

```{r}
R.Version()
```


